# Reproducible Research: Peer Assessment 1
```{r}
library(lattice)
library(ggplot2)
```
## Load the data for the propossing
```{r}
getwd()
setwd("/Users/janakiramsundaraneedi/Downloads")
data <- read.csv("activity.csv")
```

##Turn the data date into valid date class
```{r}
dates <- strptime(data$date, "%Y-%m-%d")
data$date <- dates
```
##keep all distinct days
```{r}
dates_unique <- unique(dates)
```

##Keep all the List of Possible Intervals
```{r}
unique_intervals <- unique(data$interval)
```
##Histogram of the total number of steps taken each day
```{r}
Steps_perday <- tapply(data$steps, dates$yday, FUN=sum, na.rm=TRUE)
```
##Plot the data and blue line gives Mean and green line median number of steps taken each day
```{r}
plot(dates_unique, Steps_perday, main="Histogram of steps taken each day", xlab="Date (October to November 2012)", ylab="Frequency", type="l", lwd=2, col="black")+abline(h = mean(Steps_perday), col = "blue", lwd = 3)+
abline(h = median(Steps_perday), col = "green", lwd = 3)
```
##The 5-minute interval that, on average, contains the maximum number of steps
```{r}
which.max(data$steps)
```
##Code to describe and show a strategy for imputing missing data
```{r}
table(is.na(data))
```
na_value <-  which(is.na(data))

##Fill in missing values using the average interval value across all days
```{r}
NA_value <-  which(is.na(data))
Values_Impu<-Steps_perday[as.character(data[NA_value,3])]
names(Values_Impu) <- NA_value
for (i in NA_value) {
    data$steps[i] = Values_Impu[as.character(i)]
}
sum(is.na(data))
```
## Are there differences in activity patterns between weekdays and weekends?
```{r}
wday_wend <- function(date) {
    day <- weekdays(date)
    if (day %in% c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday"))
        return("weekday")
    else if (day %in% c("Saturday", "Sunday"))
        return("weekend")
    else
        stop("invalid date")
}
data$date <- as.Date(data$date)
data$day <- sapply(data$date, FUN=wday_wend)

averages <- aggregate(steps ~ interval + day, data=data, mean)
ggplot(averages, aes(interval, steps)) + geom_line() + facet_grid(day ~ .) +
    xlab("5-minute interval") + ylab("Number of steps")
```



